---
title: "Survey Resoponses Codes"
date: "2024-04-30"
output: pdf_document
---

# Mean, Standard Deviation and Factoring the Data
Author: Aeron Jesse Edombingo

All files from rmd files folder is merged into one file and here it is.
Before running the codes please set this folder as working directory and install ggplot2, dplyr, tidyr, and gridExtra.
Thank you!
```{r}
# Import CSV file to R
filecsv <- read.csv("musicstreaming.csv")
```


```{r Performance Expectancy Mean and Standard Deviation}
# Performance Expectancy
# Find mean and standard deviation for PE1
PE1 <- filecsv$Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music..
PE1_Mean <- mean(PE1)
PE1_SD <- sd(PE1)

# Print mean and standard deviation for PE1
PE1_Mean
PE1_SD

# Find mean and standard deviation for PE2
PE2 <- filecsv$Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists.
PE2_Mean <- mean(PE2)
PE2_SD <- sd(PE2)

# Print mean and standard deviation for PE2
PE2_Mean
PE2_SD

# Find mean and standard deviation for PE3
PE3 <- filecsv$Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience.
PE3_Mean <- mean(PE3)
PE3_SD <- sd(PE3)

# Print mean and standard deviation for PE3
PE3_Mean
PE3_SD

# Find mean and standard deviation for PE4
PE4 <- filecsv$Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content.
PE4_Mean <- mean(PE4)
PE4_SD <- sd(PE4)

# Print mean and standard deviation for PE4
PE4_Mean
PE4_SD
```

```{r Effort Expectancy Mean and Standard Deviation}
# Find mean and standard deviation for EE1
EE1 <- filecsv$Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable.
EE1_Mean <- mean(EE1)
EE1_SD <- sd(EE1)

# Print mean and standard deviation for EE1
EE1_Mean
EE1_SD

# Find mean and standard deviation for EE2
EE2 <- filecsv$Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music.
EE2_Mean <- mean(EE2)
EE2_SD <- sd(EE2)

# Print mean and standard deviation for EE2
EE2_Mean
EE2_SD

# Find mean and standard deviation for EE3
EE3 <- filecsv$Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform.
EE3_Mean <- mean(EE3)
EE3_SD <- sd(EE3)

# Print mean and standard deviation for EE3
EE3_Mean
EE3_SD

# Find mean and standard deviation for EE4
EE4 <- filecsv$Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy.
EE4_Mean <- mean(EE4)
EE4_SD <- sd(EE4)

# Print mean and standard deviation for EE4
EE4_Mean
EE4_SD
```



```{r Factoring from A1 to BI3}
# Factor the responses
A1 <- factor(filecsv$Do.you.think.using.Digital.Music.Streaming.Platform.is.a.good.way.to.discover.and.enjoy.music., levels = c("Yes", "No", "Neutral"))
A2 <- factor(filecsv$Does.Digital.Music.Streaming.Platform.make.exploring.new.music.interesting.for.you., levels = c("Yes", "No", "Neutral"))
A3 <- factor(filecsv$Do.you.find.using.Digital.Music.Streaming.Platform.enjoyable., levels = c("Yes", "No", "Neutral"))
A4 <- factor(filecsv$Do.you.like.using.Digital.Music.Streaming.Platform.as.your.primary.music.streaming.service., levels = c("Yes", "No", "Neutral"))

SI1 <- factor(filecsv$Do.people.who.share.similar.music.interests.as.you.think.that.you.should.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
SI2 <- factor(filecsv$Do.people.whose.music.taste.you.respect.think.that.you.should.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
SI3 <- factor(filecsv$Has.the.endorsement.of.musicians.or.influencers.influenced.your.decision.to.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))

FC2 <- factor(filecsv$Do.you.have.a.stable.internet.connection.to.use.Digital.Music.Streaming.Platform.without.interruptions., levels = c("Yes", "No", "Neutral"))
FC3 <- factor(filecsv$Do.you.find.Digital.Music.Streaming.Platform.compatible.with.other.devices.or.platforms.you.use.for.listening.to.music., levels = c("Yes", "No", "Neutral"))
FCO1 <- factor(filecsv$Is.there.a.dedicated.support.team.available.for.assistance.with.any.issues.you.encounter.on.different.Digital.Music.Platform., levels = c("Yes", "No", "Neutral"))

SE1 <- factor(filecsv$Have.you.ever.discover.new.music.effectively.using.Digital.Music.Streaming.Platform.without.external.assistance., levels = c("Yes", "No", "Maybe"))
SE2 <- factor(filecsv$Have.you.ever.troubleshoot.and.resolve.any.technical.issues.you.encounter.on.Digital.Music.Streaming.Platform.by.yourself., levels = c("Yes", "No", "Maybe"))
SE3 <- factor(filecsv$Have.you.ever.effectively.curate.and.manage.your.music.library.on.Digital.Music.Streaming.Platform.independently., levels = c("Yes", "No", "Maybe"))

AX1 <- factor(filecsv$Do.you.feel.anxious.about.missing.out.on.new.music.releases.if.you.don.t.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
AX2 <- factor(filecsv$Does.the.thought.of.accidentally.deleting.your.playlists.or.favorite.tracks.on.Digital.Music.Streaming.Platform.make.you.feel.uneasy., levels = c("Yes", "No", "Neutral"))
AX3 <- factor(filecsv$Since.Digital.Music.Streaming.Platform.offers.features.like.playlist.backup..do.you.feel.less.anxious.about.losing.your.music.collection., levels = c("Yes", "No", "Neutral"))

BI1 <- factor(filecsv$Do.you.intend.to.continue.using.Digital.Music.Streaming.Platform.as.your.primary.music.streaming.service.in.the.next.3.months., levels = c("Yes", "No", "Maybe"))
BI2 <- factor(filecsv$Do.you.predict.you.would.explore.and.use.new.features.introduced.on.Digital.Music.Streaming.Platform.in.the.next.3.months., levels = c("Yes", "No", "Maybe"))
BI3 <- factor(filecsv$Do.you.plan.to.recommend.Digital.Music.Streaming.Platform.to.friends.or.family.members.in.the.next.3.months., levels = c("Yes", "No", "Maybe"))
```



```{r Data Frame Conversion}
# Merge responses to dataframe
mergeData <- data.frame(
  ID = c("PE1", "PE2", "PE3", "PE4", "EE1", "EE2", "EE3", "EE4"),
  Strongly_Disagree = c(sum(PE1 == 1), sum(PE2 == 1), sum(PE3 == 1), sum(PE4 == 1), sum(EE1 == 1), sum(EE2 == 1), sum(EE3 == 1), sum(EE4 == 1)),
  Disagree = c(sum(PE1 == 2), sum(PE2 == 2), sum(PE3 == 2), sum(PE4 == 2), sum(EE1 == 2), sum(EE2 == 2), sum(EE3 == 2), sum(EE4 == 2)),
  Neutral = c(sum(PE1 == 3), sum(PE2 == 3), sum(PE3 == 3), sum(PE4 == 3), sum(EE1 == 3), sum(EE2 == 3), sum(EE3 == 3), sum(EE4 == 3)),
  Agree = c(sum(PE1 == 4), sum(PE2 == 4), sum(PE3 == 4), sum(PE4 == 4), sum(EE1 == 4), sum(EE2 == 4), sum(EE3 == 4), sum(EE4 == 4)),
  Strongly_Agree = c(sum(PE1 == 5), sum(PE2 == 5), sum(PE3 == 5), sum(PE4 == 5), sum(EE1 == 5), sum(EE2 == 5), sum(EE3 == 5), sum(EE4 == 5)),
  Mean = c(PE1_Mean, PE2_Mean, PE3_Mean, PE4_Mean, EE1_Mean, EE2_Mean, EE3_Mean, EE4_Mean),
  SD = c(PE1_SD, PE2_SD, PE3_SD, PE4_SD, EE1_SD, EE2_SD, EE3_SD, EE4_SD)
)

mergeData2 <- data.frame(
  ID = c("A1", "A2", "A3", "A4", "SI1", "SI2", "SI3", "FC2", "FC3", "FCO1", "SE1", "SE2", "SE3", "AX1", "AX2", "AX3", "BI1", "BI2", "BI3"),
  Yes = c(sum(A1 == "Yes"), sum(A2 == "Yes"), sum(A3 == "Yes"), sum(A4 == "Yes"), sum(SI1 == "Yes"), sum(SI2 == "Yes"), sum(SI3 == "Yes"), sum(FC2 == "Yes"), sum(FC3 == "Yes"), sum(FCO1 == "Yes"), sum(SE1 == "Yes"), sum(SE2 == "Yes"), sum(SE3 == "Yes"), sum(AX1 == "Yes"), sum(AX2 == "Yes"), sum(AX3 == "Yes"), sum(BI1 == "Yes"), sum(BI2 == "Yes"), sum(BI3 == "Yes")),
  No = c(sum(A1 == "No"), sum(A2 == "No"), sum(A3 == "No"), sum(A4 == "No"), sum(SI1 == "No"), sum(SI2 == "No"), sum(SI3 == "No"), sum(FC2 == "No"), sum(FC3 == "No"), sum(FCO1 == "No"), sum(SE1 == "No"), sum(SE2 == "No"), sum(SE3 == "No"), sum(AX1 == "No"), sum(AX2 == "No"), sum(AX3 == "No"), sum(BI1 == "No"), sum(BI2 == "No"), sum(BI3 == "No")),
  Neutral = c(sum(A1 == "Neutral"), sum(A2 == "Neutral"), sum(A3 == "Neutral"), sum(A4 == "Neutral"), sum(SI1 == "Neutral"), sum(SI2 == "Neutral"), sum(SI3 == "Neutral"), sum(FC2 == "Neutral"), sum(FC3 == "Neutral"), sum(FCO1 == "Neutral"), sum(SE1 == "Maybe"), sum(SE2 == "Maybe"), sum(SE3 == "Maybe"), sum(AX1 == "Neutral"), sum(AX2 == "Neutral"), sum(AX3 == "Neutral"), sum(BI1 == "Maybe"), sum(BI2 == "Maybe"), sum(BI3 == "Maybe"))
)
```



```{r Write to CSV}
# Write CSV file
write.csv(mergeData, file = "Survey Data (PE1-EE4).csv", row.names = FALSE)
write.csv(mergeData2, file = "Survey Data (A1-BI3).csv", row.names = FALSE)
```



# Plotting
Author: Andrey Sumadic

```{r Load Packages}
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
```



```{r Read and Clean Data}
# Read the data
data <- read.csv("survey.csv")

# Remove rows with missing values
cleaned_data <- na.omit(data)
```



```{r Plotting Survey Answers}
# Calculate the total counts per choice for the desired column
column_counts <- cleaned_data %>%
  separate_rows(Have.you.used.any.of.these.music.streaming.platform.for.the.past.week...Can.select.multiple., sep = ", ") %>%
  group_by(Have.you.used.any.of.these.music.streaming.platform.for.the.past.week...Can.select.multiple.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_another_column <- ggplot(column_counts, aes(x = Have.you.used.any.of.these.music.streaming.platform.for.the.past.week...Can.select.multiple., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Counts per Choice for Another Column") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Calculate the total device used for the desired column
column_device <- cleaned_data %>%
  separate_rows(What.device.are.you.using.for.streaming.music.online...Can.select.multiple., sep = ", ") %>%
  group_by(What.device.are.you.using.for.streaming.music.online...Can.select.multiple.) %>%
  summarise(count = n())

# Bar graph for the total device used
bar_another_device <- ggplot(column_device, aes(x = What.device.are.you.using.for.streaming.music.online...Can.select.multiple., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Device Used") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Pie chart for age 
pie_chart_age <- ggplot(cleaned_data, aes(x = "", fill = factor(Age))) +
  geom_bar(width = 1, position = "fill") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Age",
       fill = "Age") +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )

# Pie chart for sex 
pie_chart_sex <- ggplot(cleaned_data, aes(x = "", fill = factor(Sex))) +
  geom_bar(width = 1, position = "fill") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Sex",
       fill = "Sex") +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )

# Pie chart for education level 
pie_chart_education <- ggplot(cleaned_data, aes(x = "", fill = factor(Education_level))) +
  geom_bar(width = 1, position = "fill") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Education Level",
       fill = "Education Level") +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )
```

```{r Bar Graph for PE1-EE4}
# PE1
column_countsPE1 <- cleaned_data %>%
  separate_rows(Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music.., sep = ", ") %>%
  group_by(Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music..) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnPE1 <- ggplot(column_countsPE1, aes(x = Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music.., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# PE2
column_countsPE2 <- cleaned_data %>%
  separate_rows(Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists., sep = ", ") %>%
  group_by(Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnPE2 <- ggplot(column_countsPE2, aes(x = Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# PE3
column_countsPE3 <- cleaned_data %>%
  separate_rows(Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience., sep = ", ") %>%
  group_by(Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnPE3 <- ggplot(column_countsPE3, aes(x = Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE3") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Now continuing with PE4 to EE4

# PE4
column_countsPE4 <- cleaned_data %>%
  separate_rows(Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content., sep = ", ") %>%
  group_by(Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnPE4 <- ggplot(column_countsPE4, aes(x = Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE4") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE1
column_countsEE1 <- cleaned_data %>%
  separate_rows(Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable., sep = ", ") %>%
  group_by(Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnEE1 <- ggplot(column_countsEE1, aes(x = Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE2
column_countsEE2 <- cleaned_data %>%
  separate_rows(Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music., sep = ", ") %>%
  group_by(Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnEE2 <- ggplot(column_countsEE2, aes(x = Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE3
column_countsEE3 <- cleaned_data %>%
  separate_rows(Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform., sep = ", ") %>%
  group_by(Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnEE3 <- ggplot(column_countsEE3, aes(x = Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE3") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE4
column_countsEE4 <- cleaned_data %>%
  separate_rows(Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy., sep = ", ") %>%
  group_by(Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_columnEE4 <- ggplot(column_countsEE4, aes(x = Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE4") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r}
grid.arrange(pie_chart_age,pie_chart_sex, pie_chart_education)
grid.arrange( bar_another_column, bar_another_device)
grid.arrange(bar_columnPE1, bar_columnPE2, bar_columnPE3, bar_columnPE4, bar_columnEE1, bar_columnEE2,bar_columnEE4,bar_columnEE4, nrow = 2)
```


# Creating Pie charts for A1-BI3
Author: Aeron Jesse Edombingo
```{r Create Pie Charts}
# Create Pie Chart for A1-A4
A_data <- list(
  A1 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A1 == "Yes"), sum(A1 == "No"), sum(A1 == "Neutral"))),
  
  A2 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A2 == "Yes"), sum(A2 == "No"), sum(A2 == "Neutral"))),
  
  A3 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A3 == "Yes"), sum(A3 == "No"), sum(A3 == "Neutral"))),
  
  A4 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A4 == "Yes"), sum(A4 == "No"), sum(A4 == "Neutral")))
)

A_plots <- lapply(names(A_data), function(name) {
  data <- A_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = A_plots, ncol = 2, top = "Attitude toward using Digital Music Streaming Platform")

# Create Pie Chart for SI1-SI3
SI_data <- list(
  SI1 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(SI1 == "Yes"), sum(SI1 == "No"), sum(SI1 == "Neutral"))),
  
  SI2 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(SI2 == "Yes"), sum(SI2 == "No"), sum(SI2 == "Neutral"))),
  
  SI3 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(SI3 == "Yes"), sum(SI3 == "No"), sum(SI3 == "Neutral")))
)

SI_plots <- lapply(names(SI_data), function(name) {
  data <- SI_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = SI_plots, ncol = 2, top = "Social Influence")

# Create Pie Chart for FC2-FC01
FC_data <- list(
  FC2 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(FC2 == "Yes"), sum(FC2 == "No"), sum(FC2 == "Neutral"))),
  
  FC3 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(FC3 == "Yes"), sum(FC3 == "No"), sum(FC3 == "Neutral"))),
  
  FCO1 = data.frame(Response = c("Yes", "No", "Neutral"),
                    Frequency = c(sum(FCO1 == "Yes"), sum(FCO1 == "No"), sum(FCO1 == "Neutral")))
)

FC_plots <- lapply(names(FC_data), function(name) {
  data <- FC_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = FC_plots, ncol = 2, top = "Facilitating Conditions")

# Create Pie Chart for SE1-SE3
SE_data <- list(
  SE1 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(SE1 == "Yes"), sum(SE1 == "No"), sum(SE1 == "Maybe"))),
  
  SE2 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(SE2 == "Yes"), sum(SE2 == "No"), sum(SE2 == "Maybe"))),
  
  SE3 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(SE3 == "Yes"), sum(SE3 == "No"), sum(SE3 == "Maybe")))
)

SE_plots <- lapply(names(SE_data), function(name) {
  data <- SE_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = SE_plots, ncol = 2, top = "Self-Efficacy")

# Create Pie Chart for AX1-AX3
AX_data <- list(
  AX1 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(AX1 == "Yes"), sum(AX1 == "No"), sum(AX1 == "Neutral"))),
  
  AX2 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(AX2 == "Yes"), sum(AX2 == "No"), sum(AX2 == "Neutral"))),
  
  AX3 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(AX3 == "Yes"), sum(AX3 == "No"), sum(AX3 == "Neutral")))
)

AX_plots <- lapply(names(AX_data), function(name) {
  data <- AX_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = AX_plots, ncol = 2, top = "Anxiety")

# Create Pie Chart for BI1-BI3
BI_data <- list(
  BI1 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(BI1 == "Yes"), sum(BI1 == "No"), sum(BI1 == "Maybe"))),
  
  BI2 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(BI2 == "Yes"), sum(BI2 == "No"), sum(BI2 == "Maybe"))),
  
  BI3 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(BI3 == "Yes"), sum(BI3 == "No"), sum(BI3 == "Maybe")))
)

BI_plots <- lapply(names(BI_data), function(name) {
  data <- BI_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = BI_plots, ncol = 2, top = "Behavioral Intention")
```