---
title: "Survey Resoponses Codes"
date: "2024-04-30"
output: pdf_document
---

# Mean, Standard Deviation and Factoring the Data
Author: Aeron Jesse Edombingo

All files from rmd files folder is merged into one file and here it is.
Before running the codes please set this folder as working directory and install ggplot2, dplyr, tidyr, and gridExtra.
Thank you!
```{r}
# Import CSV file to R
filecsv <- read.csv("musicstreaming.csv")
```


```{r Performance Expectancy Mean and Standard Deviation}
# Performance Expectancy
# Find mean and standard deviation for PE1
PE1 <- filecsv$Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music..
PE1_Mean <- mean(PE1)
PE1_SD <- sd(PE1)

# Print mean and standard deviation for PE1
PE1_Mean
PE1_SD

# Find mean and standard deviation for PE2
PE2 <- filecsv$Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists.
PE2_Mean <- mean(PE2)
PE2_SD <- sd(PE2)

# Print mean and standard deviation for PE2
PE2_Mean
PE2_SD

# Find mean and standard deviation for PE3
PE3 <- filecsv$Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience.
PE3_Mean <- mean(PE3)
PE3_SD <- sd(PE3)

# Print mean and standard deviation for PE3
PE3_Mean
PE3_SD

# Find mean and standard deviation for PE4
PE4 <- filecsv$Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content.
PE4_Mean <- mean(PE4)
PE4_SD <- sd(PE4)

# Print mean and standard deviation for PE4
PE4_Mean
PE4_SD
```

```{r Effort Expectancy Mean and Standard Deviation}
# Find mean and standard deviation for EE1
EE1 <- filecsv$Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable.
EE1_Mean <- mean(EE1)
EE1_SD <- sd(EE1)

# Print mean and standard deviation for EE1
EE1_Mean
EE1_SD

# Find mean and standard deviation for EE2
EE2 <- filecsv$Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music.
EE2_Mean <- mean(EE2)
EE2_SD <- sd(EE2)

# Print mean and standard deviation for EE2
EE2_Mean
EE2_SD

# Find mean and standard deviation for EE3
EE3 <- filecsv$Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform.
EE3_Mean <- mean(EE3)
EE3_SD <- sd(EE3)

# Print mean and standard deviation for EE3
EE3_Mean
EE3_SD

# Find mean and standard deviation for EE4
EE4 <- filecsv$Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy.
EE4_Mean <- mean(EE4)
EE4_SD <- sd(EE4)

# Print mean and standard deviation for EE4
EE4_Mean
EE4_SD
```



```{r Factoring from A1 to BI3}
# Factor the responses in Attitude
A1 <- factor(filecsv$Do.you.think.using.Digital.Music.Streaming.Platform.is.a.good.way.to.discover.and.enjoy.music., levels = c("Yes", "No", "Neutral"))
A2 <- factor(filecsv$Does.Digital.Music.Streaming.Platform.make.exploring.new.music.interesting.for.you., levels = c("Yes", "No", "Neutral"))
A3 <- factor(filecsv$Do.you.find.using.Digital.Music.Streaming.Platform.enjoyable., levels = c("Yes", "No", "Neutral"))
A4 <- factor(filecsv$Do.you.like.using.Digital.Music.Streaming.Platform.as.your.primary.music.streaming.service., levels = c("Yes", "No", "Neutral"))

# Factor the responses in Social Influence then get the Mean and Standard Deviation
SI1 <- factor(filecsv$Do.people.who.share.similar.music.interests.as.you.think.that.you.should.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
SI1_recoded <- recode(SI1, "Yes" = 1, "No" = 2, "Neutral" = 3)
SI1_Mean <- mean(SI1_recoded)
SI1_SD <- sd(SI1_recoded)
SI1_Mean
SI1_SD

SI2 <- factor(filecsv$Do.people.whose.music.taste.you.respect.think.that.you.should.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
SI2_recoded <- recode(SI2, "Yes" = 1, "No" = 2, "Neutral" = 3)
SI2_Mean <- mean(SI2_recoded)
SI2_SD <- sd(SI2_recoded)
SI2_Mean
SI2_SD

SI3 <- factor(filecsv$Has.the.endorsement.of.musicians.or.influencers.influenced.your.decision.to.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
SI3_recoded <- recode(SI3, "Yes" = 1, "No" = 2, "Neutral" = 3)
SI3_Mean <- mean(SI3_recoded)
SI3_SD <- sd(SI3_recoded)
SI3_Mean
SI3_SD

# Factor the responses in Facilitating Condition then get the Mean and Standard Deviation
# We started from FC2 because SI3 is duplicated as FC1 in the questionnaire, FCO1 is Other.
FC2 <- factor(filecsv$Do.you.have.a.stable.internet.connection.to.use.Digital.Music.Streaming.Platform.without.interruptions., levels = c("Yes", "No", "Neutral"))
FC2_recoded <- recode(FC2, "Yes" = 1, "No" = 2, "Neutral" = 3)
FC2_Mean <- mean(FC2_recoded)
FC2_SD <- sd(FC2_recoded)
FC2_Mean
FC2_SD

FC3 <- factor(filecsv$Do.you.find.Digital.Music.Streaming.Platform.compatible.with.other.devices.or.platforms.you.use.for.listening.to.music., levels = c("Yes", "No", "Neutral"))
FC3_recoded <- recode(FC3, "Yes" = 1, "No" = 2, "Neutral" = 3)
FC3_Mean <- mean(FC3_recoded)
FC3_SD <- sd(FC3_recoded)
FC3_Mean
FC3_SD

FCO1 <- factor(filecsv$Is.there.a.dedicated.support.team.available.for.assistance.with.any.issues.you.encounter.on.different.Digital.Music.Platform., levels = c("Yes", "No", "Neutral"))
FCO1_recoded <- recode(FCO1, "Yes" = 1, "No" = 2, "Neutral" = 3)
FCO1_Mean <- mean(FCO1_recoded)
FCO1_SD <- sd(FCO1_recoded)
FCO1_Mean
FCO1_SD

SE1 <- factor(filecsv$Have.you.ever.discover.new.music.effectively.using.Digital.Music.Streaming.Platform.without.external.assistance., levels = c("Yes", "No", "Maybe"))
SE2 <- factor(filecsv$Have.you.ever.troubleshoot.and.resolve.any.technical.issues.you.encounter.on.Digital.Music.Streaming.Platform.by.yourself., levels = c("Yes", "No", "Maybe"))
SE3 <- factor(filecsv$Have.you.ever.effectively.curate.and.manage.your.music.library.on.Digital.Music.Streaming.Platform.independently., levels = c("Yes", "No", "Maybe"))

AX1 <- factor(filecsv$Do.you.feel.anxious.about.missing.out.on.new.music.releases.if.you.don.t.use.Digital.Music.Streaming.Platform., levels = c("Yes", "No", "Neutral"))
AX2 <- factor(filecsv$Does.the.thought.of.accidentally.deleting.your.playlists.or.favorite.tracks.on.Digital.Music.Streaming.Platform.make.you.feel.uneasy., levels = c("Yes", "No", "Neutral"))
AX3 <- factor(filecsv$Since.Digital.Music.Streaming.Platform.offers.features.like.playlist.backup..do.you.feel.less.anxious.about.losing.your.music.collection., levels = c("Yes", "No", "Neutral"))

BI1 <- factor(filecsv$Do.you.intend.to.continue.using.Digital.Music.Streaming.Platform.as.your.primary.music.streaming.service.in.the.next.3.months., levels = c("Yes", "No", "Maybe"))
BI2 <- factor(filecsv$Do.you.predict.you.would.explore.and.use.new.features.introduced.on.Digital.Music.Streaming.Platform.in.the.next.3.months., levels = c("Yes", "No", "Maybe"))
BI3 <- factor(filecsv$Do.you.plan.to.recommend.Digital.Music.Streaming.Platform.to.friends.or.family.members.in.the.next.3.months., levels = c("Yes", "No", "Maybe"))
```



```{r Data Frame Conversion}
# Group
PE_means <- c(PE1_Mean, PE2_Mean, PE3_Mean, PE4_Mean)
PE_SDs <- c(PE1_SD, PE2_SD, PE3_SD, PE4_SD)

EE_means <- c(EE1_Mean, EE2_Mean, EE3_Mean, EE4_Mean)
EE_SDs <- c(EE1_SD, EE2_SD, EE3_SD, EE4_SD)

SI_means <- c(SI1_Mean, SI2_Mean, SI3_Mean)
SI_SDs <- c(SI1_SD, SI2_SD, SI3_SD)

FC_means <- c(FC2_Mean, FC3_Mean, FCO1_Mean)
FC_SDs <- c(FC2_SD, FC3_SD, FCO1_SD)

# Find the Total Means and Mean of Standard Deviation of each group
PE_total_mean <- mean(PE_means)
PE_total_SD_mean <- mean(PE_SDs)

EE_total_mean <- mean(EE_means)
EE_total_SD_mean <- mean(EE_SDs)

SI_total_mean <- mean(SI_means)
SI_total_SD_mean <- mean(SI_SDs)

FC_total_mean <- mean(FC_means)
FC_total_SD_mean <- mean(FC_SDs)

# Create data frames
PE_data <- data.frame(ID = "PE", Name = "Performance Expectancy", Mean = PE_means, SD = PE_SDs)
EE_data <- data.frame(ID = "EE", Name = "Effort Expectancy", Mean = EE_means, SD = EE_SDs)
SI_data <- data.frame(ID = "SI", Name = "Social Influence", Mean = SI_means, SD = SI_SDs)
FC_data <- data.frame(ID = "FC", Name = "Facilitating Conditions", Mean = FC_means, SD = FC_SDs)

# Write data frames to CSV files
write.csv(PE_data, "PE_data.csv", row.names = FALSE)
write.csv(EE_data, "EE_data.csv", row.names = FALSE)
write.csv(SI_data, "SI_data.csv", row.names = FALSE)
write.csv(FC_data, "FC_data.csv", row.names = FALSE)

# Create data frames for combined factors
Factors_means <- c(PE_total_mean, EE_total_mean, SI_total_mean, FC_total_mean)
Factors_SDs <- c(PE_total_SD_mean, EE_total_SD_mean, SI_total_SD_mean, FC_total_SD_mean)
Factor_names <- c("Performance Expectancy", "Effort Expectancy", "Social Influence", "Facilitating Conditions")

Factors_data <- data.frame(ID = c("PE", "EE", "SI", "FC"), Name = Factor_names, Mean = Factors_means, SD = Factors_SDs)

# Write combined factors CSV file
write.csv(Factors_data, "Combined_factors.csv", row.names = FALSE)

```



# Plotting
Author: Andrey Sumadic

```{r Load Packages}
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
```



```{r Read and Clean Data}
# Read the data
data <- read.csv("survey.csv")

# Remove rows with missing values
cleaned_data <- na.omit(data)
```



```{r Plotting Survey Answers}
# Calculate the total counts per choice for the desired column
column_counts <- cleaned_data %>%
  separate_rows(Have.you.used.any.of.these.music.streaming.platform.for.the.past.week...Can.select.multiple., sep = ", ") %>%
  group_by(Have.you.used.any.of.these.music.streaming.platform.for.the.past.week...Can.select.multiple.) %>%
  summarise(count = n())

# Bar graph for the total counts per choice
bar_another_column <- ggplot(column_counts, aes(x = Have.you.used.any.of.these.music.streaming.platform.for.the.past.week...Can.select.multiple., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Counts per Choice for Another Column") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Calculate the total device used for the desired column
column_device <- cleaned_data %>%
  separate_rows(What.device.are.you.using.for.streaming.music.online...Can.select.multiple., sep = ", ") %>%
  group_by(What.device.are.you.using.for.streaming.music.online...Can.select.multiple.) %>%
  summarise(count = n())

# Bar graph for the total device used
bar_another_device <- ggplot(column_device, aes(x = What.device.are.you.using.for.streaming.music.online...Can.select.multiple., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "Device Used") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Pie chart for age 
pie_chart_age <- ggplot(cleaned_data, aes(x = "", fill = factor(Age))) +
  geom_bar(width = 1, position = "fill") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Age",
       fill = "Age") +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )

# Pie chart for sex 
pie_chart_sex <- ggplot(cleaned_data, aes(x = "", fill = factor(Sex))) +
  geom_bar(width = 1, position = "fill") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Sex",
       fill = "Sex") +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )

# Pie chart for education level 
pie_chart_education <- ggplot(cleaned_data, aes(x = "", fill = factor(Education_level))) +
  geom_bar(width = 1, position = "fill") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Education Level",
       fill = "Education Level") +
  theme_void() +
  theme(
    plot.title = element_text(hjust = 0.5)
  )
```

```{r Bar Graph for PE1-EE4}
# PE1
column_countsPE1 <- cleaned_data %>%
  separate_rows(Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music.., sep = ", ") %>%
  group_by(Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music..) %>%
  summarise(count = n())

# Bar graph for PE1
bar_columnPE1 <- ggplot(column_countsPE1, aes(x = Do.you.find.using.Digital.Music.Streaming.Platform.useful.in.discovering.new.music.., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# PE2
column_countsPE2 <- cleaned_data %>%
  separate_rows(Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists., sep = ", ") %>%
  group_by(Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists.) %>%
  summarise(count = n())

# Bar graph for PE2
bar_columnPE2 <- ggplot(column_countsPE2, aes(x = Does.Digital.Music.Streaming.Platform.enable.you.to.easily.create.and.share.playlists., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# PE3
column_countsPE3 <- cleaned_data %>%
  separate_rows(Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience., sep = ", ") %>%
  group_by(Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience.) %>%
  summarise(count = n())

# Bar graph for PE3
bar_columnPE3 <- ggplot(column_countsPE3, aes(x = Do.you.believe.that.using.Digital.Music.Streaming.Platform.will.enhance.your.overall.music.listening.experience., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE3") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# PE4
column_countsPE4 <- cleaned_data %>%
  separate_rows(Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content., sep = ", ") %>%
  group_by(Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content.) %>%
  summarise(count = n())

# Bar graph for PE4
bar_columnPE4 <- ggplot(column_countsPE4, aes(x = Do.you.think.using.Digital.Music.Streaming.Platform.will.increase.your.engagement.with.music.related.content., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "PE4") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE1
column_countsEE1 <- cleaned_data %>%
  separate_rows(Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable., sep = ", ") %>%
  group_by(Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable.) %>%
  summarise(count = n())

# Bar graph for EE1
bar_columnEE1 <- ggplot(column_countsEE1, aes(x = Do.you.find.navigating.through.Digital.Music.Streaming.Platform.clear.and.understandable., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE2
column_countsEE2 <- cleaned_data %>%
  separate_rows(Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music., sep = ", ") %>%
  group_by(Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music.) %>%
  summarise(count = n())

# Bar graph for EE2
bar_columnEE2 <- ggplot(column_countsEE2, aes(x = Do.you.find.Digital.Music.Streaming.Platform.easy.to.use.in.terms.of.searching.for.and.playing.music., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE3
column_countsEE3 <- cleaned_data %>%
  separate_rows(Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform., sep = ", ") %>%
  group_by(Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform.) %>%
  summarise(count = n())

# Bar graph for EE3
bar_columnEE3 <- ggplot(column_countsEE3, aes(x = Do.you.believe.it.would.be.easy.for.you.to.become.skilled.in.using.Digital.Music.Streaming.Platform., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE3") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# EE4
column_countsEE4 <- cleaned_data %>%
  separate_rows(Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy., sep = ", ") %>%
  group_by(Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy.) %>%
  summarise(count = n())

# Bar graph for EE4
bar_columnEE4 <- ggplot(column_countsEE4, aes(x = Do.you.find.learning.to.use.Digital.Music.Streaming.Platform.easy., y = count)) +
  geom_bar(stat = "identity") +
  labs(title = "EE4") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r}
grid.arrange(pie_chart_age,pie_chart_sex, pie_chart_education)
# Most respondents are from the age range of 18-25. 
# Most respondents are male.
# Most respondents are College students.
grid.arrange( bar_another_column, bar_another_device)
# Most of the respondents use Spotify as their music online streaming platform. 
# Most of the respondents use Smartphone to stream music on their favorite music platform.
grid.arrange(bar_columnPE1, bar_columnPE2, bar_columnPE3, bar_columnPE4, bar_columnEE1, bar_columnEE2,bar_columnEE4,bar_columnEE4, nrow = 2)
# Most of the respondents strongly agrees that they have positive experience performance wise 
# on their music streaming platform.

# Most respondents find it convenient to use their music streaming platform.
```


# Creating Pie charts for A1-BI3
Author: Aeron Jesse Edombingo
```{r Create Pie Charts}
# Create Pie Chart for A1-A4
A_data <- list(
  A1 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A1 == "Yes"), sum(A1 == "No"), sum(A1 == "Neutral"))),
  
  A2 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A2 == "Yes"), sum(A2 == "No"), sum(A2 == "Neutral"))),
  
  A3 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A3 == "Yes"), sum(A3 == "No"), sum(A3 == "Neutral"))),
  
  A4 = data.frame(Response = c("Yes", "No", "Neutral"),
                  Frequency = c(sum(A4 == "Yes"), sum(A4 == "No"), sum(A4 == "Neutral")))
)

A_plots <- lapply(names(A_data), function(name) {
  data <- A_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = A_plots, ncol = 2, top = "Attitude toward using Digital Music Streaming Platform")
# Most of the respondents agrees that their music streaming platform are enjoyable and interesting.


# Create Pie Chart for SI1-SI3
SI_data <- list(
  SI1 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(SI1 == "Yes"), sum(SI1 == "No"), sum(SI1 == "Neutral"))),
  
  SI2 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(SI2 == "Yes"), sum(SI2 == "No"), sum(SI2 == "Neutral"))),
  
  SI3 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(SI3 == "Yes"), sum(SI3 == "No"), sum(SI3 == "Neutral")))
)

SI_plots <- lapply(names(SI_data), function(name) {
  data <- SI_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = SI_plots, ncol = 2, top = "Social Influence")
# Most of the respondents share the same interests and influenced by other people.

# Create Pie Chart for FC2-FC01
FC_data <- list(
  FC2 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(FC2 == "Yes"), sum(FC2 == "No"), sum(FC2 == "Neutral"))),
  
  FC3 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(FC3 == "Yes"), sum(FC3 == "No"), sum(FC3 == "Neutral"))),
  
  FCO1 = data.frame(Response = c("Yes", "No", "Neutral"),
                    Frequency = c(sum(FCO1 == "Yes"), sum(FCO1 == "No"), sum(FCO1 == "Neutral")))
)

FC_plots <- lapply(names(FC_data), function(name) {
  data <- FC_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = FC_plots, ncol = 2, top = "Facilitating Conditions")
# Most of the respondents have stable internet, compatible devices and a technical support to address issues on their music streaming platform.


# Create Pie Chart for SE1-SE3
SE_data <- list(
  SE1 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(SE1 == "Yes"), sum(SE1 == "No"), sum(SE1 == "Maybe"))),
  
  SE2 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(SE2 == "Yes"), sum(SE2 == "No"), sum(SE2 == "Maybe"))),
  
  SE3 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(SE3 == "Yes"), sum(SE3 == "No"), sum(SE3 == "Maybe")))
)

SE_plots <- lapply(names(SE_data), function(name) {
  data <- SE_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = SE_plots, ncol = 2, top = "Self-Efficacy")
# Most of the students have the knowledge and skills to address their issues on their music streaming platform.


# Create Pie Chart for AX1-AX3
AX_data <- list(
  AX1 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(AX1 == "Yes"), sum(AX1 == "No"), sum(AX1 == "Neutral"))),
  
  AX2 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(AX2 == "Yes"), sum(AX2 == "No"), sum(AX2 == "Neutral"))),
  
  AX3 = data.frame(Response = c("Yes", "No", "Neutral"),
                   Frequency = c(sum(AX3 == "Yes"), sum(AX3 == "No"), sum(AX3 == "Neutral")))
)

AX_plots <- lapply(names(AX_data), function(name) {
  data <- AX_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = AX_plots, ncol = 2, top = "Anxiety")

# Missing Out on New Music Releases:
# Most respondents voted “No.” They don’t feel anxious about missing out on new music releases if they don’t use a Digital Music Streaming Platform.

# Accidental Playlist or Track Deletion:
# Most respondents voted “Yes.” The thought of accidentally deleting playlists or favorite tracks on a Digital Music Streaming Platform makes them feel uneasy.

# Playlist Backup and Anxiety Reduction:
# Most respondents voted “Yes.” The availability of features like playlist backup on Digital Music Streaming Platforms helps reduce anxiety about losing their music collection.

# Create Pie Chart for BI1-BI3
BI_data <- list(
  BI1 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(BI1 == "Yes"), sum(BI1 == "No"), sum(BI1 == "Maybe"))),
  
  BI2 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(BI2 == "Yes"), sum(BI2 == "No"), sum(BI2 == "Maybe"))),
  
  BI3 = data.frame(Response = c("Yes", "No", "Maybe"),
                   Frequency = c(sum(BI3 == "Yes"), sum(BI3 == "No"), sum(BI3 == "Maybe")))
)

BI_plots <- lapply(names(BI_data), function(name) {
  data <- BI_data[[name]]
  ggplot(data, aes(x = "", y = Frequency, fill = Response)) +
    geom_bar(stat = "identity") +
    coord_polar("y", start = 0) +
    labs(title = name,
         fill = "Response") +
    theme_void() +
    theme(legend.position = "bottom")
})

grid.arrange(grobs = BI_plots, ncol = 2, top = "Behavioral Intention")

# Continued Usage:
# Most respondents voted “Yes.” They intend to continue using Digital Music Streaming Platforms as their primary music streaming service in the next 3 months.

# Exploring New Features:
# Most respondents voted “Yes.” They predict that they would explore and use new features introduced on Digital Music Streaming Platforms in the next 3 months.

# Recommendations:
# Most respondents voted “Yes.” They plan to recommend Digital Music Streaming Platforms to friends or family members in the next 3 months.
```